The Thresholding Bandit Problem

### 2017-05-14 Thresholding Bandit/ThresholdingBandit.tex
initial commit

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Theorems and Proofs},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Theorems and Proofs}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{4/23/2017}

@@

\subsection{Theorem 1}\label{theorem-1}

In Theorem 1 of Locatelli et al. (2016), a lower bound for the
thresholding bandit problem is shown. The basic idea is as follows. The
problem formulation considered in the paper describes bandit problems
for Sub-Gaussian distributions. To show a lower bound, we show that
every algorithm is expected to make a certain error even if we restrict
ourselves to a heavily specified scenario. Even then, any algorithm will
have a certain level of risk with which it cannot distinguish between
the actual setting and a slightly changed setting (under which the
former answer leads to regret).

To be more specific, consider a case in which we set \(\tau = 0\) and
\(\epsilon = 0\) w.l.o.g. If we then choose all arms to have normally
distributed feedback with means \(\mu_i\), we see that for each arm
\(i\) the distance from the threshold is given by
\(\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i\). Thus, assuming a
variance of 1 for every arm, we have for every arm the distribution
\(\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)\). Furthermore,
define \(\nu_i' = \mathcal{N}(-\Delta_i,1)\).

The idea now is that every arm \(i \in \{1,\dots,K\}\) generates a
sample for every time point \(t\in \{1, \dots, T\}\) from its
distribution \(\nu_i\) before the algorithm starts to choose arms. Thus,
we have a \(T \times K\) table of realized observations from the product
distribution given by
\(\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K\).
This is a product distribution where the \(K\) different means all lie
above the threshold. We would hope that an algorithm classifies the
means accordingly. However, we will show in what follows that any
algorithm makes a certain error by not being able to distinguish
\(\mathcal{B}^0\) from a product distribution \(\mathcal{B}^i\) which
differs only slightly and has the same overall complexity (as defined by
\(H = \sum_{i=1}^K (\Delta_i)^{-2}\)).

Before the start of the algorithm, we introduce a slight variation in
the setup. Similar to how one can switch arms in the pure exploration
setup for multi-armed bandits (compare Audibert et al., Garivier \&
Kaufmann) to ``confuse'' the algorithm without introducing additional
complexity to the specified problem. However, since we do not compare
arms with each other directly in the thresholding bandit problem
(switching arms would still keep all means above the threshold), we
instead need to flip an arm with respect to the threshold. Since the
threshold is \(\tau = 0\), we have for the flipped arm the new
distribution \(\nu_i'\) as defined above. Indeed, we can define the new
product distribution \(B^i = \nu_1^i \otimes \dots \otimes \nu_K^i\)
where for
\(k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}\).
This flipping of the arm corresponds to multiplying all random variables
\(X_{i,t}\) of arm \(i\) by \(-1\).

As in Locatelli et al. (2016), we let for \(i \leq K\),
\(\mathbb{P}_{\mathcal{B}^i}\) define the probability distribution
describing all samples that a bandit strategy can potentially collect up
to horizon \(T\), i.e.~according to the samples
\((X_{k,s})_{k\leq K, s \leq T} \sim (\mathcal{B}^i)^{\otimes T}\).
\((T_k)_{k\leq K}\) denotes the number of samples collected on arm \(k\)
until time \(T\).

\paragraph{Reminder about the goal of the
proof}\label{reminder-about-the-goal-of-the-proof}

At this point, we have defined a finite set of problems of Gaussian
distributions with fixed variance 1 for a given set of set of gaps
between the means of the distributions and the threshold, \((d_k)_k\).
We will now proof a lower bound on the worst case regret of any
algorithm; that is, the maximum error probability that even the best
algorithm makes on this problem.

\paragraph{Statistical Decision}\label{statistical-decision}

Given our formulation of the regret, the expected regret
\(\mathbb{E}[\mathcal{L}(T)]\) corresponds directly to the probability
of making a wrong classification of any of the \(K\) means. In general,
let \(T\) be a binary decision function, and define
\(\Omega = \{T = 0\}\) and \(\Omega^C = \{T = 1\}\). Assume that the
decision \(T\) distinguishes between two states of the world, \(H_0\)
and \(H_1\). Then our overall error probability is given by
\(P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)\).

In our case, \(H_0\) may correspond to the state in which we have
\(\mathcal{B}^0\), and \(H_1\) corresponds to the case where any arm has
been flipped, \(\mathcal{B}^i\). Furthermore, we consider the events in
which the algorithm, making the decision, classifies arm \(i\) as being
above the threshold: \(\mathcal{A}_i = \{i \in \hat{S}_\tau\). The event
on which all arms are being classified as above the threshold is
consequently given by \(\mathcal{A} = \bigcap \mathcal{A}_i\). However,
Theorem 1 does not bound the overall regret, but the maximum error
probability. We can write this now as

\begin{equation}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{equation}

In order to give a bound on above equation, we start by considering
\(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\). This probability can be
measured as the expected change in the likelihood of observed data times
the probability under the original state. The measure of event
\(\mathcal{A}_i\) under state \(\mathcal{B}^i\) is given as the
probability of \(\mathcal{A}_i\) under the (original) state
\(\mathcal{B}^0\) multiplied by a factor. This factor is the change in
the data likelihoods due to moving from \(\mathcal{B}^0\) to
\(\mathcal{B}^i\), and is expressed as the expected likelihood ratio
under \(\mathcal{B}^0\). By definition though, this is equal to the
empirical Kullback-Leibler divergence of the two measures.

First, let us define the change of measure in terms of the empirical
log-likelihood for our case. Then, we will show how to replace the
log-likelihood by the empirical Kullback-Leibler divergence.

Let every \(\nu_i, \nu_i'\) be dominated by the Lebesgue measure
\(\lambda\). Then their density functions are given by
\(f_i = \frac{\der \nu_i}{\der \lambda}\) and
\(f_i' = \frac{\der \nu_i'}{\der \lambda}\) respectively. For
\(T \geq t \geq 0\), define the empirical Kullback-Leibler divergence as

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log(\frac{\der \nu_k'}{\der \nu_k}(X_{k,s})) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& = \frac{1}{t} \log \big( \prod_{s=1}^{t} \frac{f_k'(X_{k,s})}{f_k(X_{k,s})} \big) \\
& \stackrel{\text{iid}}{=} \frac{1}{t} \log \big( \frac{f_k'(X_{k,1}, \dots,X_{k,t})}{f_k(X_{k,1}, \dots,X_{k,t})} \big) \\
& = \frac{1}{t} \log \big( \text{LR}((X_{k,1}, \dots,X_{k,t}), \nu_k', \nu_k) \big)
\end{align*}

Since we consider Gaussian distributions with variance 1, we have
density functions
\(f_i(x) \propto \exp \big(-\frac{1}{2} (x-\Delta_i)^2\big)\) and
\(f_i'(x) \propto \exp \big(-\frac{1}{2} (x+\Delta_i)^2\big)\). Plugging
this into the above definition of the empirical Kullback-Leibler
divergence, we easily see

\begin{align*}
\hat{\KL}_{k,t} & = \frac{1}{t} \sum_{s=1}^{t} \log \big(\frac{\exp \big(-\frac{1}{2} (X_{k,s}+\Delta_k)^2\big)}{\exp \big(-\frac{1}{2} (X_{k,s}-\Delta_k)^2\big)} \big) \\
& = \frac{1}{t} \sum_{s=1}^{t} \log \big( \exp(-\frac{1}{2} (X_{k,s}+\Delta_k)^2 + \frac{1}{2} (X_{k,s}-\Delta_k)^2) \big) \\
& = - \frac{1}{t} \sum_{s=1}^{t} 2 X_{k,s} \Delta_k
\end{align*}

\paragraph{Change of Measure}\label{change-of-measure}

We are now ready to state the change of measure. As alluded to above, we
consider how the probability changes for the event \(\mathcal{A}_i\)
when we move from \(\mathcal{B}^0\) to \(\mathcal{B}^i\). When flipping
arm \(i\), we only changed the samples of this arm, that is, the first
\(T_i\) observations we got from arm \(i\) the algorithm took. The
change of measure is then defined as:

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \text{LR}((X_{i,1}, \dots,X_{i,T_i}), \nu_i', \nu_i) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ]
\end{align*}

Obviously, \(\hat{\KL}_{i,T_i}\) depends on the realized samples
\(X_{i,1}, \dots,X_{i,T_i}\). Consequently, we need to find a bound on
\(\hat{\KL}_{i,T_i}\) itself to incorporate the uncertainty involved in
this metric.

\paragraph{Kullback-Leibler
Divergence}\label{kullback-leibler-divergence}

For our problem, the Kullback-Leibler divergence of \(/nu_k'\) from
\(\nu_k\) is given by \(\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2\).

\paragraph{Concentration of the Empirical Kullback-Leibler
Divergence}\label{concentration-of-the-empirical-kullback-leibler-divergence}

It is easy to see that

\begin{equation*}
|\hat{\KL}_{k,t} - \KL_{k,t}| = |-\frac{2}{t} \Delta_k \sum_{s=1}^{t}(X_{k,s} - \Delta_k)|
\end{equation*}

itself is a normally distributed random variable with mean zero and a
variance decreasing in \(t\). Thus, one can show that
\(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\) for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
\end{equation}

Thus, in order to bound the empirical Kullback-Leibler divergence in our
change of measure, we can consider the intersection of \(\mathcal{A}_i\)
and \(\xi\) as follows and plug in the bound on event \(\xi\):

\begin{align*}
\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- T_i \hat{\KL}_{i,T_i}) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

Two things are left to do: With \(T_i\), we still have one random
variable left which we cannot leave in our bound. Second, we are
actually not interested in \(\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)
but in
\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\).

\paragraph{\texorpdfstring{Bounding \(T_i\) for
\(\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\)}{Bounding T\_i for \textbackslash{}max\_\{i \textbackslash{}in \textbackslash{}\{1,\textbackslash{}dots,K\textbackslash{}\}\}\textbackslash{}mathbb\{P\}\_\{\textbackslash{}mathcal\{B\}\^{}i\}(\textbackslash{}mathcal\{A\}\_i)}}\label{bounding-t_i-for-max_i-in-1dotskmathbbp_mathcalbimathcala_i}

Part of our bound is
\(\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)\),
so let's continue with that. In general it holds that
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\). Thus we can
write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of \(\mathcal{A}_i\) and
\(\xi\) as before in order to apply the change of measure again in the
third line.

What is left to show before we have our final bound is a bound on
\(T_i\). To show that any algorithm has a certain bound on its error, it
only makes sense that every arm has to pulled at least a certain amount
of times. Consequently, no arm should be pulled exclusively.

First, let \(a = \Delta_i \sqrt{T_i}\) and
\(b = 4\sqrt{\log((4\log(T)+1)K)}\). Then use \(ab \leq a^2 + b^2\) to
write \(ab \leq \Delta_i^2 T_i + 16\log((4\log(T)+1)K)\). And so:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) ]
\end{align*}

Furthermore, we know that the sum of the individual arm pulls has to be
equal to the overall number of pulls (equal to the budget in the fixed
budget sense), \(\sum_i T_i = T\), and furthermore we know that
\(T_i>0\). The latter holds since any reasonable algorithm has to check
each arm at least once in our setup. This is because we need to check
each arm's performance in comparison to the threshold. Thus it is easy
to show that
\(\exists i: T_i \leq \frac{T}{H \Delta_i^2} = \frac{T}{(\sum_{i=1}^{K} \Delta_i^{-2}) \Delta_i^2}\).
To see this, assume the opposite:
\(\forall i: T_i > T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2}\). This
implies however
\(\sum_{i=1}^K T_i > \sum_{i=1}^K T \frac{\sum_{i=1}^K \Delta_i^2}{\Delta_i^2} = T \cdot 1 = T\)
which is a contradiction.

So we can write \((\Delta_i \sqrt{T_i})^2 \leq \frac{T}{H}\). We use
\(\mathcal{A} = \cap_{i=1}^K \mathcal{A}_i\) to write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}{K} \exp (- 3 \Delta_i^2 T_i - 16 \log(4(\log(T)+1)K)) \big]
\end{align*}

We write
\(\frac{1}{K} \sum_{i=1}^K \exp(-3T_i \Delta_i^2) \geq \frac{1}{K} \sum_{i=1}^K \exp(-3 T/H) = \exp(-3 T/H)\).
Thus:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \Delta_i^2 T_i) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& \geq \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \frac{1}{K} \sum_{i=1}^{K} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A} \cap \xi} \exp (- 3 \frac{T}{H}) \exp(-16 \log(4(\log(T)+1)K)) ] \\
& = \mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

\paragraph{Conclusion}\label{conclusion}

Consider again the risk which we need to bound from equation
\eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss
over all \(\mathcal{B}_i\). By again using the fact that in general
\(\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}\), we plug in
our previous calculations:

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \label{LocatelliTheorem1DefinitionOfRisk}
\end{align}

From \eqref{LocatelliTheorem1EventXi} we know that for any
\(i \in \{0, \dots, K\}\), \(\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4\).
Following the argument in Locatelli et al. (2016), we now consider two
cases: \(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\). In the former
case, we can plug in the two probabilities into
\eqref{LocatelliTheorem1DefinitionOfRisk}. If
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \geq 1/2\) and
\(\mathbb{P}_{\mathcal{B}^0}(\xi) \geq 3/4\), then
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \geq 1/4\). Thus:

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq \frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) + \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \\
& \geq \frac{1}{8} \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K))
\end{align*}

where we drop the second summand of the second line so that the
inequality holds.

On the other hand, when
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \leq 1/2\), then we know that
\(\mathbb{P}_{\mathcal{B}^0}(\mathcal{A} \cap \xi) \leq 1/2\) for any
\(\mathbb{P}_{\mathcal{B}^0}(\xi)\). At the same time
\(1-\mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \geq 1/2\).
Consequently,
\(1/4 \leq \frac{1}{2}(1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A})) \leq 1/2\),
while
\(\frac{1}{2}\mathbb{P}_{\mathcal{B}^0} (\mathcal{A} \cap \xi) \exp (- 3 \frac{T}{H} -16 \log(4(\log(T)+1)K)) \geq 0\).
And so the stronger lower bound in that case is, as noticed by Locatelli
et al. (2016), given simply by

\begin{align*}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \\
& \geq 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) = \mathbb{P}_{\mathcal{B}^0}(\mathcal{A^C}) \\
& \geq \frac{1}{2}
\end{align*}

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={The Thresholding Bandit Problem},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{The Thresholding Bandit Problem}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Tim Radtke}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{4/23/2017}

@@

The \emph{Thresholding Bandit Problem} described in Locatelli et al.
(2016) can be considered a variant of a variant. It can be framed into
the wider literature of \emph{Pure Exploration} multi-armed bandit
problems. In particular, it shares characteristics with the
\emph{Top-\(m\)} problem. This problem is concerned with finding the
\(m\) best arms as described by the means of their corresponding
distributions. This in turn is similar to the \emph{combinatorial
bandit} problem, which also aims at finding the \(m\) best arms.
However, it is able to pull several arms at once: Think of an online
shop that shows five recommended products on a product detail page.
These five recommended products might each be represented by an arm, and
we look for the products with the largest mean conversion rate. The
thresholding bandit problem we discuss here, however, is concerned with
pulling a single arm at a time. And so a more appropriate situation is
that of a website presenting a banner. Again, think of an online shop
trying to promote a certain category. The content team came up with a
number of different designs for the banner, and it's not clear how many
click-throughs they will gather.

The idea now is that we would like to classify the banners into two
distinct groups: A group with a mean conversion rate \(\mu_i\) below
threshold \(\tau\), and a group with mean conversion rate \(\mu_i\)
above threshold \(\tau\). This might be the optimization problem when we
are concerned with not falling below a certain minimum level
click-through rate with the banners we're choosing.

If it turns out that in general we can find relatively quickly whether
arms are above or below a threshold, then this kind of test can be used
to safeguard against very bad versions in a test. Before we move to a
Top-\(m\) test, we might want to run a thresholding version and then
continue only with the arms classified into the group above the
threshold. This might be justified when adjusting parts of the checkout
process of an online shop, where the conversion rate or the average
order value should not drop below a threshold.

\subsection{Setup}\label{setup}

In any case, the problem boils down to the following. As standard in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed accoring to the arm's distribution \(\nu_k\). In general, we
are concerned with estimating for each arm \(i\) the mean \(\mu_i\) of
its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. In the case of pure exploration bandits, it is for example
necessary to compare the arms because one aims to find the best one. In
the case of the thresholding bandit, however, we compare each arm's mean
\(\mu_i\) individually against the threshold \(\tau \in \mathbb{R}\)
which is known and fixed before the experiment. One might compare this
to a pure exploration bandit in which the mean of the best arm is known
upfront. We will see later that this fact leads to advantages in the
design of algorithms which are not as readily available in other bandit
settings.
